### 2020-01-28 2020/WCGO_MCO_OptimizationLetters/2020_WCGO_MCO.tex
исправил форматирование таблиц

\begin{table}[ht]
\centering
\caption{Results of the series of experiments to solve two-dimensional two-criteria MCO problems}
\label{tab:2}
\resizebox{\columnwidth}{!}{
\begin{tabular}{ccccccccc}
\hline
\multicolumn{8}{c}{Search information}                                    & Reduction \\ \cline{1-8}
\multicolumn{4}{c}{not used}       & \multicolumn{4}{c}{used}             &  in \\ \cline{1-8}
Method     & Problem & Avg   & Avg   & Method     & Problem & Avg   & Avg   & iteration    \\
iter.      & solved  & HV    & DU    & iter.      & solved  & HV    & DU    & number       \\ \hline
41 710.1   & 98.0\%  & 33.43 & 0.173 & 2 407.41   & 99.3\%  & 33.34 & 0.224 & 17.3         \\ \hline
\end{tabular}
}
\end{table}

@@

\begin{table}[ht]
\centering
\caption{Results of the series of experiments to solve two-criteria four-dimensional MCO}
\label{tab:3}
\resizebox{\columnwidth}{!}{
\begin{tabular}{ccccccccc}
\hline
\multicolumn{8}{c}{Search information}                                    & Reduction \\ \cline{1-8}
\multicolumn{4}{c}{not used}       & \multicolumn{4}{c}{used}             &  in \\ \cline{1-8}
Method      & Problem & Avg   & Avg   & Method     & Problem & Avg   & Avg   & iteration    \\
iter.       & solved  & HV    & DU    & iter.      & solved  & HV    & DU    & number       \\ \hline
4 536 377.9 & 83.0\%  & 30.67 & 0.335 & 709 014.9  & 94.5\%  & 30.46 & 0.405 & 6.4         \\ \hline
\end{tabular}
}
\end{table}

>>>>

\begin{table}[ht]
\centering
\caption{Results of the series of experiments to solve two-dimensional two-criteria MCO problems}
\label{tab:2}
\resizebox{\columnwidth}{!}{
\begin{tabular}{ccccccccccc}
\hline
\multicolumn{10}{c}{Search information}                                    & Reduction \\ \cline{1-9}
\multicolumn{4}{c}{not used}         & & \multicolumn{4}{c}{used}             &  & in \\ \cline{1-4} \cline{6-9}
Method     & Problem & Avg   & Avg   & & Method     & Problem & Avg   & Avg   &  & iteration    \\
iter.      & solved  & HV    & DU    & & iter.      & solved  & HV    & DU    &  & number       \\ \cline{1-4} \cline{6-9} \cline{11-11}
41 710.1   & 98.0\%  & 33.43 & 0.173 & & 2 407.41   & 99.3\%  & 33.34 & 0.224 &  & 17.3         \\ \hline
\end{tabular}
}
\end{table}

@@

\begin{table}[ht]
\centering
\caption{Results of the series of experiments to solve two-criteria four-dimensional MCO}
\label{tab:3}
\resizebox{\columnwidth}{!}{
\begin{tabular}{ccccccccccc}
\hline
\multicolumn{10}{c}{Search information}                                        & Reduction   \\ \cline{1-9}
\multicolumn{4}{c}{not used}       & & \multicolumn{4}{c}{used}                & &  in       \\ \cline{1-4} \cline{6-9}
Method      & Problem & Avg   & Avg   & & Method     & Problem & Avg   & Avg   & & iteration \\
iter.       & solved  & HV    & DU    & & iter.      & solved  & HV    & DU    & & number    \\ \cline{1-4} \cline{6-9} \cline{11-11}
4 536 377.9 & 83.0\%  & 30.67 & 0.335 & & 709 014.9  & 94.5\%  & 30.46 & 0.405 & & 6.4       \\ \hline
\end{tabular}
}
\end{table}
